Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-02-28 paper/main.tex
added info about choosing number of topics and refs to new supp fig

We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
each moment of the two lectures and each question in our pool in a common
representational space. Briefly, our approach uses a topic model (Latent
Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set of documents, to
discover a set of $k$ ``topics'' or ``themes.'' Formally, each topic is defined
as a set of weights over each word in the model's vocabulary (i.e., the union
of all unique words, across all documents, excluding ``stop words.'').
Conceptually, each topic is intended to give larger weights to words that are
semantically related or tend to co-occur in the same documents. After
fitting a topic model, each document in the training set, or any \textit{new}
document that contains at least some of the words in the model's vocabulary,
may be represented as a $k$-dimensional vector describing how much the document
(most probably) reflects each topic. (Unless, otherwise noted, we used $k = 15$
topics.)

>>>>

We adapted an approach we developed in prior work~\citep{HeusEtal21} to embed
each moment of the two lectures and each question in our pool in a common
representational space. Briefly, our approach uses a topic model (Latent
Dirichlet Allocation;~\citealp{BleiEtal03}), trained on a set of documents, to
discover a set of $k$ ``topics'' or ``themes.'' Formally, each topic is defined
as a set of weights over each word in the model's vocabulary (i.e., the union
of all unique words, across all documents, excluding ``stop words.'').
Conceptually, each topic is intended to give larger weights to words that are
semantically related or tend to co-occur in the same documents. After
fitting a topic model, each document in the training set, or any \textit{new}
document that contains at least some of the words in the model's vocabulary,
may be represented as a $k$-dimensional vector describing how much the document
(most probably) reflects each topic.
To select an appropriate $k$ for our model, we identified the minimum number of
topics that yielded at least one ``unused'' topic (i.e., in which all words in the vocabulary
were assigned zero weight) after training. This indicated that the number of topics was
sufficient to capture the set of latent themes present in the two lectures (from which we
constructed our document corpus, as described below). We found this value to be $k = 15$
topics. The distribution of weights over words in the vocabulary for each discovered topic is
shown in Supplementary Figure~\topicWordWeights, and each topic's top-weighted
words may be found in Supplementary Table~\topics.
